Classless Java

### 2015-11-04 paper/sections/RelatedWork.tex
related work on multiple inheritance

There are proposals for extending Java with traits. For example, FeatherTrait
Java (FTJ)~\cite{Liquori08ftj} by Liquori et al. extends the calculus of
Featherweight Java (FJ)~\cite{Igarashi01FJ} with statically-typed traits, adding
trait-based inheritance in Java. \yanlin{Drawbacks to be added...}

\paragraph{Multiple Inheritance}
Traits~\cite{} and mixins~\cite{} provides novel models of new programming
architecture in object oriented programming paradim. As shown in
section~\ref{sec:comparison}, although they solved some multiple inheritance
problems, they are extremely restricting expressiveness.

- traits (original, variations, scala)
- mixins (original, scala)
- c++ solution : virtual inheritance
- multiple inheritance
- ...

\paragraph{ThisType/MyType/Extensibility}

>>>>

\yanlin{need to discuss: whether the comments for FTJ is fair.}
There are proposals for extending Java with traits. For example, FeatherTrait
Java (FTJ)~\cite{Liquori08ftj} by Liquori et al. extends the calculus of
Featherweight Java (FJ)~\cite{Igarashi01FJ} with statically-typed traits, adding
trait-based inheritance in Java. However, language extensions (including FTJ)
have a natural drawback: the programmer has to learn new syntax. In contrast,
our approach is completely compatible with the current Java language, so that
programmers don't need to pay any learning cost to adapt to this new classless
programming pattern. Another drawback which is particular for FTJ is that FTJ
doesn't have type for traits, hence the correctness check of trait is done when
type-checking classes. This choice makes the design of FTJ simpler but lost
typechecking efficiency (one trait will be potentially checked multiple times if
it is used in multiple classes).

\subsection{Multiple Inheritance in General}
Multiple inheritance is a great feature to have in a programming language, but
it is difficult to model and implement. These difficulties include the famous
diamond (fork-join) problem, conflicting methods, yo-yo problem, etc. In order
to model multiple inheritance, lots of models have been proposed in the past few
years, including mixins~\cite{bracha90mixin} and traits~\cite{scharli03traits}.
Both traits and mixins provide novel models of new programming architecture in
object oriented programming paradigm.

1) Mixins model named components that can be applied to various classes as
reusable functionality units. However, the well-known limitation of mixins is
that they suffer from linearization constraints, which hinders the
expressiveness of mixins and the ability of resolving conflicts.  As shown in
section~\ref{sec:comparison}, although they solved some multiple inheritance
problems, they are extremely restricting expressiveness.

2) Traits are a novel model to differentiate two functionalities out of classes:
units of reusable components and object factories. In trait models, traits are
responsible for units of reusable components, which contain pure methods as
reusable functionalities; whereas classes act as object factories, which
requires various functionalities from multiple traits. However drawbacks of
traits are obvious: traits do not allow state; traits can't be instantiated
directly.

3) C++ and Scala also try to provide solutions to multiple inheritance, but both
suffer from object initialization problems. Virtual inheritance in C++ provides
another solution to multiple inheritance (especially the diamond problem by
keeping only one copy of the base class)~\cite{ellis1990annotated}, however
suffers from object initialization problem as pointed out by Malayeri et
al.~\cite{malayeri2009cz}. It bypasses all constructor calls to virtual
superclasses, which would potentially cause serious semantic error. Scala
solution (traits) avoids this problem by disallowing constructor parameters,
causing no ambiguity in cases such as diamond problem. The drawback of this
elegant design is limited expressiveness.

\paragraph{ThisType/MyType/Extensibility}
\emph{This} is a polymorphic type variable.  Typical Type Systems
forClass-Based Object-Oriented PLs. Class names as types.  Inheritance as
subtyping Resulting in difficulty in reusing classes with recursive interfaces
by inheritance Standard (non)solution: downcasts Self types (often called MyType
[Bruce et al.])  OCaml

Does our approach support binary methods?
